Initial Analysis

### 2019-09-17 Initial_Analysis.Rmd
Discrete stocks

  # Load and clean Discrete results
  Discrete_Data <- fread(paste(Results_Path,"/Trans_Results/Non_Transboundary_Data.csv",sep="")) %>% 
    filter(!is.na(TaxonKey)) %>% 
    select(2:3)

@@

Transboundary_Spp <- Clean_Results_Trans %>% 
  filter(
         Area_Index >= Min_AI,
         Area_Index <= Max_AI,
         Model_Index == MI
         ) %>% 
  group_by(Territory) %>% 
  summarise(
    n_trans_spp = length(unique(TaxonKey)),
    n_Neighbours = length(unique(Neighbour)),
    Trans_Rate = n_trans_spp/n_Neighbours
    )

### Non-transboundary
# 
# Partial_Transboundary_Spp <- Clean_Results_Trans %>% 
#   filter(
#          Area_Index >= Min_AI,
#          Area_Index <= Max_AI,
#          Model_Index == MI
#          ) 
# 
# Discrete_Spp_Area_Index <- Clean_Results_Trans %>% 
#   filter(
#     Area_Index >= Max_AI, # Discrete spp only on countryes with > 75%
#     # Area_Index <= Min_AI,
#          Model_Index == MI
#          ) %>% 
#   anti_join(Partial_Transboundary_Spp, # Removes species if it is already transboundary in a country
#             by = c("TaxonKey","Territory")
#   ) %>% 
#   group_by(Territory) %>% 
#   summarise(
#     n_discrete_spp = length(unique(TaxonKey))
    )

# Discrete_Spp <- Discrete_Data %>% 
#   group_by(Territory) %>% 
#   summarise(
#     n_discrete_spp = length(unique(TaxonKey))
#     ) %>% 
#   bind_rows(Discrete_Spp_Area_Index) %>% 
#   group_by(Territory) %>% 
#   summarise(n_discrete = sum(n_discrete_spp))

  # Merging eezs by territories (e.g. Mex Atlantic and pacific to Mez)
Country_Discrete_Data <- Discrete_Data %>% 
  rename(eez_name = Territory) %>% 
  left_join(sau_eez_fes) %>% 
  group_by(Territory = fishing_entity) %>% 
  summarise(value = length(unique(TaxonKey)))

@@

@@

Catch_Country <- Sau_Catch_Data %>% 
  group_by(FishingRegion=Territory) %>% 
  summarise(Total_Catch = round(sum(Mean_Catch,na.rm=T)/1000000,2)) %>% 
  filter(!(is.na(FishingRegion))) %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(Territory = fishing_entity) %>% 
  summarise(Total_Catch = sum(Total_Catch,na.rm=T)) %>% 
  mutate(Territory = gsub("USA","United States of America",Territory))

World_sf_si_land <- World_land_sf %>%
  st_transform(crs = 4326) %>% # 4326
  # st_transform(crs = "+proj=wintri") %>% # tubed world
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%  # Include transboundary species
  left_join(Catch_Country, by ="Territory") # Include total specices catch

@@

World_sf_si$Bins <- cut(World_sf_si$n_trans_spp,breaks = 5)
World_sf_si_land$BinsLan <- cut(World_sf_si_land$Total_Catch,breaks = 5)

# unique(World_sf_si$Bins)
# unique(World_sf_si_land$BinsLan)

@@

Plot <- ggplot() +
  geom_sf(data = World_sf_si_land,aes(fill = BinsLan), colour = "grey80") +
  geom_sf(data = World_sf_si,aes(fill = Bins),colour = "grey20") + # n_trans_spp or Bins
  geom_sf(data = Grey_land,aes(fill = BinsLan),fill = "grey80") + # n_trans_spp or Bins
  # scale_fill_gradientn(colours = pal,
  #                      na.value = "white") +
  scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
                               rev(wes_palette(n = 5, name = "Darjeeling2"))
                               ),
                     na.value = "white"
  ) +
  # scale_fill_manual("",values = c("#5BBCD6","#5BBCD6","#00A08A","#00A08A","#F2AD00","#F2AD00","#F98400","#FF0000","#FF0000","#FF0000"),
  #                    na.value = "white"
  # ) +
  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
  #                    na.value = "white"
  # ) +
  ggtheme_map()

@@

Countries_Data <- Clean_Results_Trans %>% 
  filter(
    Area_Index >= Min_AI,
    Area_Index <= Max_AI,
    Model_Index == MI
  ) %>% 
  group_by(Territory = CT_fishing_entity) %>% 
  summarise(value = length(unique(TaxonKey))) %>% 
  left_join(UN_Regions, by ="Territory") %>%
  mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
  rename(FishingRegion=Territory) %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(individual = fishing_entity,group) %>% 
  summarise(Total_trans = sum(value,na.rm=T)) %>% 
  mutate(value = ifelse(Total_trans > 100,100,Total_trans)) %>% 
  filter(!is.na(individual)) %>% 
  select(individual,group,value) %>% 
  arrange(group,value)

@@

Discrete_Data <- Clean_Results_Trans %>% 
  filter(Model_Index == MI) %>% 
  ## Determine as Trans. those species that are both trans and discrete for a nation (Tresh 2 and 3)
  mutate(Species_Type = ifelse(Area_Index > Max_AI,"Discrete",
                                ifelse(Area_Index < Min_AI,NA,
                                "Transboundary"))
         ) %>% 
  filter(!is.na(Species_Type)) %>% 
  group_by(CT_fishing_entity,Species_Type,TaxonKey) %>%
  summarise(n=n()) %>%
  spread(Species_Type,n) %>% 
  mutate(Discrete = ifelse(!is.na(Discrete) & !is.na(Transboundary),NA,Discrete)) %>% 
  gather("Species_Type","value", Discrete:Transboundary) %>% 
  filter(!is.na(value),
         Species_Type == "Discrete") %>% 
  group_by(Territory = CT_fishing_entity) %>% 
  summarise(value = length(unique(TaxonKey)),
            Taxons = paste(unique(TaxonKey),collapse = ";")) %>% 
  #  Include discrete species of Trsh. 1
  bind_rows(Country_Discrete_Data) %>%
  # Data cleaning (group by territory and include georegions for plot)
  rename(FishingRegion=Territory) %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(Territory = fishing_entity) %>% 
  summarise(value =sum(value,na.rm = T)*-1) %>% # Multyply them by -1 so they appear negative on plot
  mutate(value = ifelse(value <= -100,-100,value)) %>% 
  left_join(UN_Regions, by ="Territory") %>%
  mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
  filter(!is.na(Territory)) %>% 
  select(individual = Territory,
         group,
         value)

# Include possible missing countries in bothe datasets
Countries_Data <- Discrete_Data %>% 
  anti_join(Countries_Data,
            by = c("individual","group")) %>% 
  mutate(Total_Discrete = 0) %>% 
  bind_rows(Countries_Data)

Discrete_Data <- Countries_Data %>% 
  anti_join(Discrete_Data,
            by = c("individual","group")) %>% 
  mutate(value = 0) %>% 
  bind_rows(Discrete_Data)

@@

# Set a number of 'empty bar' to add at the end of each group
Char <- as.factor(Countries_Data$group) # Set groups to factors
empty_bar <- length(unique(Countries_Data$group))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char), ncol(Countries_Data)) )
colnames(to_add) <- colnames(Countries_Data)
to_add$group <- rep(levels(Char), each=empty_bar)
Countries_Data <- bind_rows(Countries_Data, to_add)
Countries_Data <- Countries_Data %>% arrange(group,value)
Countries_Data$id <- seq(1, nrow(Countries_Data))

@@

# Top n of each group label
Top_Countries <- Countries_Data %>% 
  group_by(group) %>% 
  top_n(5,value)

@@

# prepare a data frame for base lines
base_data <- Countries_Data %>% 
  group_by(group) %>% 
  summarize(start=min(id), 
            end=max(id) - empty_bar, 
            median = median(value, na.rm = T)
            ) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

@@

Discrete_Data_Plot <- Discrete_Data %>% 
  left_join(Countries_Data,
            by =c("individual","group")
  ) %>%
  mutate(value = ifelse(value.x <= -100,-100,value.x)) %>%
  select(individual,group,value,id) %>%
  arrange(group,value)

@@

Discrete_Data_Plot %>% 
  anti_join(Countries_Data,
            by = c("individual","group","id"))

@@

# Global Variables
Seq_axis <- seq(-100,100,20)
Plot_Limit <- max(Countries_Data$value,na.rm=T)
Plot_Limit_Low <- -110
Ticks_Color <- "grey50"

@@

ggplot(Countries_Data,

@@

           x = rep(max(Countries_Data$id),length(Seq_axis)),

@@

```{Tran_country, eval =F, echo =F}

# Number of Transboundary Species
length(unique(Clean_Results_Trans$TaxonKey)) #664 spp

# Number of Discret EEZ species

# Ge those stocks that are not trans due to Area_Index
length(unique(Results_Discrete$TaxonKey))

@@

# Number of countries shared by each Species
Species_Trans <- Clean_Results_Trans %>% 
  filter(
         Area_Index < Min_AI |
         Area_Index > Max_AI,
         Model_Index == MI
         ) %>% 
  group_by(TaxonKey) %>% 
  summarise(
    n_countries = length(unique(Territory))
  ) %>% 
  left_join(Exploited_Species) %>%
  left_join(Spp_Clasification)

@@

Species_Data <- Clean_Results_Trans %>% 
  filter(
         Area_Index >= Min_AI,
         Area_Index <= Max_AI,
         Model_Index == MI#,
         # Same_Nation == "No"
         ) %>% 
  group_by(TaxonKey) %>% 
  summarise(n_trans_spp = length(unique(Territory))) %>% 
  left_join(Exploited_Species) %>%
  rename(scientific_name = TaxonName) %>% 
  left_join(Species_environ_list) %>%
  mutate(DemersPelag = ifelse(is.na(DemersPelag),"Other",paste(DemersPelag)),
         n_trans_spp = ifelse(n_trans_spp > 100, 100, n_trans_spp)) %>% 
  select(individual=scientific_name,
         value = n_trans_spp,
         group = DemersPelag) %>% 
  arrange(group,value) %>% 
  filter(value > 10) # remove all species under 10 (way too many to plot!)

@@

# Make the plot
ggplot(Species_Data, 
       aes(x=as.factor(id), 
           y=value,
           fill=group)
       ) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
  geom_bar(aes(x=as.factor(id),
               y=value,
               fill=group),
           stat="identity",
           alpha=0.5) +
  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  # Add median lines for each gropup
  geom_segment(data=median_data, aes(x = end, y = median, xend = start+5, yend = median, colour = group),
               alpha=1, size=0.5 , inherit.aes = FALSE ) +
  # geom_hline(yintercept = Median_trans, colour = "black", alpha=1, size=0.3,linetype="dashed") + # All groups median
  # Add text showing the value of each line
  annotate("text", 
           x = rep(max(Species_Data$id),5),
           y = c(20, 40, 60, 80, 100),
           label = c("20", "40", "60","80",">100"),
           color="grey", 
           size=3 , 
           angle=0, 
           fontface="bold",
           hjust=1) +
  geom_bar(aes(x=as.factor(id),
               y=value,
               fill=group),
           stat="identity",
           alpha=0.5) +
  geom_text(data=label_data_rest,
            aes(x=id, y=110,
                label=individual,
                hjust=hjust), 
            color="black",
            # fontface="bold",
            alpha=0.6,
            size=2.5,
            angle= label_data_rest$angle,
            inherit.aes = FALSE) +
  # Bold top 3 
  geom_text(data=Top_label_data,
            aes(x=id, y=110,
                label=individual,
                hjust=hjust), 
            color="black",
            fontface="bold",
            alpha=0.6,
            size=2.5,
            angle= Top_label_data$angle,
            inherit.aes = FALSE) +
  # Add base line information
  geom_segment(data=base_data, 
               aes(x = start, 
                   y = -5, 
                   xend = end, 
                   yend = -5
                   ), 
               colour = "black",
               alpha=0.8, 
               size=0.6 , 
               inherit.aes = FALSE) +
  ylim(-140,140) + # sets the circle the first value the central the last value how wide
  theme_minimal() +
  theme(
    legend.position = c(0.5,0.5),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm") 
  ) +
  coord_polar() + 
  scale_fill_manual("Ecosystem Preference",
                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
                               wes_palette(n = 4, name = "Darjeeling2")
                    ),
                    na.value = "white"
  ) +
  scale_colour_manual("Ecosystem Preference",
                      values = c(wes_palette(n = 5, name = "Darjeeling1"),
                                 wes_palette(n = 4, name = "Darjeeling2")
                      ),
                      na.value = "white"
  )
# 
# ggsave(
#     plot = last_plot(),
#     width = 14,
#     height = 10,
#     units = "in",
#     filename = "Species_circular_over10.tiff",
#     path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
#   )

@@

### Potential connections Map

```{r connection_map, eval = F, echo = F}

# https://www.data-to-viz.com/story/MapConnection.html

# Load dataset from github (Surfer project)
data <- read.table("https://github.com/holtzy/data_to_viz/raw/master/Example_dataset/19_MapConnection.csv", header=T, sep=",")

head(data)
Clean_Results <- read.csv("~/GitHub/FishForVisa/Temporal_Data/Clean_Results.csv")

Clean_Results <- Clean_Results %>% 
  select(TaxonKey, homename = Country_Territory, travelname = Neighbor_Territory)

library(readxl)
EEZIDs_List <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")
EEZ_CellID <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/EEZ_CellID.xlsx")

# DBEM Coordinate system
Coor <- read.csv("~/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/Lon_Lat_DBEM.txt",header = FALSE)
colnames(Coor) <- c("INDEX","Longitude","Latitude")

Index_Code <- EEZIDs_List %>% 
  left_join(EEZ_CellID) %>% 
  rename(Territory = Name) %>% 
  left_join(Coor, by = "INDEX") %>% 
  group_by(Territory) %>% 
  summarise(Latitude = mean(Latitude),
            Longitude = mean(Longitude)
  )

Home_coor <- Index_Code %>% 
  rename(
    homename = Territory,
    homelat = Latitude,
    homelon = Longitude)

Travel_coor <- Index_Code %>% 
  rename(
    travelname = Territory,
    travellat = Latitude,
    travellon = Longitude)

# Download NASA night lights image
download.file("https://www.nasa.gov/specials/blackmarble/2016/globalmaps/BlackMarble_2016_01deg.jpg", 
              destfile = "BlackMarble_2016_01deg.jpg", mode = "wb")
# Load picture and render
earth <- jpeg::readJPEG("BlackMarble_2016_01deg.jpg", native = TRUE)
earth <- grid::rasterGrob(earth, interpolate = TRUE)

# Count how many times we have each unique connexion + order by importance
summary=data %>% 
  dplyr::count(homelat,homelon,homecontinent, travellat,travellon,travelcontinent) %>%
  arrange(n)

summary <- Data %>%
  group_by(homename,travelname) %>% 
  summarise(n = n()) %>% 
  left_join(Home_coor) %>% 
  left_join(Travel_coor)

# A function that makes a dateframe per connection (we will use these connections to plot each lines)
data_for_connection=function( dep_lon, dep_lat, arr_lon, arr_lat, group){
  inter <- geosphere::gcIntermediate(c(dep_lon, dep_lat), c(arr_lon, arr_lat), n=50, addStartEnd=TRUE, breakAtDateLine=F)             
  inter=data.frame(inter)
  inter$group=NA
  diff_of_lon=abs(dep_lon) + abs(arr_lon)
  if(diff_of_lon > 180){
    inter$group[ which(inter$lon>=0)]=paste(group, "A",sep="")
    inter$group[ which(inter$lon<0)]=paste(group, "B",sep="")
  }else{
    inter$group=group
  }
  return(inter)
}

# Création d'un dataframe complet avec les points de toutes les lignes à faire.
data_ready_plot=data.frame()
for(i in c(1:nrow(summary))){
tmp=data_for_connection(summary$homelon[i], summary$homelat[i], summary$travellon[i], summary$travellat[i] , i)
  # tmp$homecontinent=summary$homecontinent[i]
  tmp$n=summary$n[i]
  data_ready_plot=rbind(data_ready_plot, tmp)
}

data_ready_plot$homecontinent=factor(data_ready_plot$homecontinent, levels=c("Asia","Europe","Australia","Africa","North America","South America","Antarctica"))

# Plot
library(ggplot2)
pal <- wesanderson::wes_palette("Zissou1", 1000, type = "continuous")
ggplot() +
  annotation_custom(earth, xmin = -180, xmax = 180, ymin = -90, ymax = 90) +
  geom_line(data=data_ready_plot, aes(x=lon,
                                      y=lat, 
                                      group=group,
                                      colour=n
                                      )
            ) +
  # scale_color_brewer(palette="Set3") +
  scale_colour_gradientn(colours = pal) +
  theme_void() +
  theme(
    legend.position="bottom",
    panel.background = element_rect(fill = "black", colour = "black"), 
    panel.spacing=unit(c(0,0,0,0), "null"),
    plot.margin=grid::unit(c(0,0,0,0), "cm")
    ) +
  xlim(-180,180) +
  ylim(-60,80) +
  scale_x_continuous(expand = c(0.006, 0.006)) +
  coord_equal()

````

# Problem solving

>>>>

  # Load and clean Discrete results
  Non_Transboundary_Data <- fread(paste(Results_Path,"/Trans_Results/Non_Transboundary_Data.csv",sep="")) %>% 
    filter(!is.na(TaxonKey)) %>% 
    select(2:3)

@@

Tresholded_T_Data <- Clean_Results_Trans %>% 
  filter(
         Area_Index >= Min_AI,
         Area_Index <= Max_AI,
         Model_Index == MI
         )

### Non-transboundary Tresh 1
Clean_Non_Transboundary_Data <- Non_Transboundary_Data %>% 
  rename(eez_name = Territory) %>% 
  left_join(sau_eez_fes) %>% 
  group_by(Territory = fishing_entity) %>% 
  summarise(value = length(unique(TaxonKey)),
            Taxons = paste(unique(TaxonKey),collapse = ";"))

## Determine as Trans. those species that are both trans and discrete for a nation (Tresh 2 and 3)
Tresholded_D_Data <- Clean_Results_Trans %>% 
  filter(Model_Index == MI) %>% 
  mutate(Species_Type = ifelse(Area_Index > Max_AI,"Discrete",
                                ifelse(Area_Index < Min_AI,NA,
                                "Transboundary"))
         ) %>% 
  filter(!is.na(Species_Type)) %>% 
  group_by(CT_fishing_entity,Species_Type,TaxonKey) %>%
  summarise(n=n()) %>%
  spread(Species_Type,n) %>% 
  mutate(Discrete = ifelse(!is.na(Discrete) & !is.na(Transboundary),NA,Discrete)) %>% 
  gather("Species_Type","value", Discrete:Transboundary) %>% 
  filter(!is.na(value),
         Species_Type == "Discrete") %>% 
  group_by(Territory = CT_fishing_entity) %>% 
  summarise(value = length(unique(TaxonKey)),
            Taxons = paste(unique(TaxonKey),collapse = ";")) %>% 
  #  Include discrete species of Trsh. 1
  bind_rows(Clean_Non_Transboundary_Data) %>%
  # Data cleaning (group by territory and include georegions for plot)
  rename(FishingRegion=Territory) %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(Territory = fishing_entity)

@@

```{r Data_per_Territory}

# Data per Territory
Transboundary_Spp <- Tresholded_Data %>% 
  group_by(Territory) %>% 
  summarise(
    n_trans_spp = length(unique(TaxonKey)),
    n_Neighbours = length(unique(Neighbour)),
    Trans_Rate = n_trans_spp/n_Neighbours
    )

# Number of Transboundary Species
Total_trans_n <- Clean_Results_Trans %>% 
  filter(
         Area_Index >= Min_AI,
         Area_Index <= Max_AI,
         Model_Index == MI
         )

length(unique(Total_trans_n$TaxonKey)) #674 spp

@@

Catch_Country <- Sau_Catch_Data %>% 
  group_by(FishingRegion=Territory) %>% 
  summarise(Total_Catch = round(sum(Mean_Catch,na.rm=T),2)) %>% 
  filter(!(is.na(FishingRegion))) %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(Territory = fishing_entity) %>% 
  summarise(Total_Catch = sum(Total_Catch,na.rm=T)) %>% 
  mutate(Territory = gsub("USA","United States of America",Territory))

World_sf_si_land <- World_land_sf %>%
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%  # Include transboundary species
  left_join(Catch_Country, by ="Territory") # Include total specices catch

@@

World_sf_si$Bins <- cut(World_sf_si$n_trans_spp,breaks = 4)
World_sf_si_land$Bins <- cut(World_sf_si_land$Total_Catch,breaks = 4)

head(World_sf_si)
head(World_sf_si_land)

unique(World_sf_si$Bins)
unique(World_sf_si_land$BinsLan)

@@

Plot <- ggplot() +
  geom_sf(data = World_sf_si_land,aes(fill = BinsLan), colour = "grey80") +
  geom_sf(data = World_sf_si,aes(fill = Bins),colour = "grey20") + # n_trans_spp or Bins
  geom_sf(data = Grey_land,aes(fill = BinsLan),fill = "grey80") + # n_trans_spp or Bins
  # scale_fill_gradientn(colours = pal,
  #                      na.value = "white") +
  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
                               # rev(wes_palette(n = 4, name = "Darjeeling2"))
                               # ),
                     # na.value = "white"
  # ) +
  scale_fill_manual("",values = c("#5BBCD6","#5BBCD6","#00A08A","#00A08A","#F2AD00","#F2AD00","#FF0000","#FF0000"),
                     na.value = "white"
  ) +
  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
  #                    na.value = "white"
  # ) +
  ggtheme_map()

@@

Countries_Data_Plot <- Tresholded_Data %>% 
  group_by(Territory = CT_fishing_entity) %>% 
  summarise(value = length(unique(TaxonKey))) %>% 
  left_join(UN_Regions, by ="Territory") %>%
  mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
  rename(FishingRegion=Territory) %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(individual = fishing_entity,group) %>% 
  summarise(Total_trans = sum(value,na.rm=T)) %>% 
  mutate(value = ifelse(Total_trans > 100,100,Total_trans)) %>% 
  filter(!is.na(individual)) %>% 
  select(individual,group,value) %>% 
  arrange(group,value)

@@

Discrete_Data_Plot <- Tresholded_D_Data %>% 
  summarise(value =sum(value,na.rm = T)*-1) %>% # Multyply them by -1 so they appear negative on plot
  mutate(value = ifelse(value <= -100,-100,value)) %>% 
  left_join(UN_Regions, by ="Territory") %>%
  mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
  filter(!is.na(Territory)) %>% 
  select(individual = Territory,
         group,
         value)

# Include possible missing countries in bothe datasets
Countries_Data_Plot <- Discrete_Data_Plot %>% 
  anti_join(Countries_Data_Plot,
            by = c("individual","group")) %>% 
  mutate(Total_Discrete = 0) %>% 
  bind_rows(Countries_Data_Plot)

Discrete_Data_Plot <- Countries_Data_Plot %>% 
  anti_join(Discrete_Data_Plot,
            by = c("individual","group")) %>% 
  mutate(value = 0) %>% 
  bind_rows(Discrete_Data_Plot)

@@

# Set a number of 'empty bar' to add at the end of each group
Char <- as.factor(Countries_Data_Plot$group) # Set groups to factors
empty_bar <- length(unique(Countries_Data_Plot$group))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char), ncol(Countries_Data_Plot)) )
colnames(to_add) <- colnames(Countries_Data_Plot)
to_add$group <- rep(levels(Char), each=empty_bar)
Countries_Data_Plot <- bind_rows(Countries_Data_Plot, to_add)
Countries_Data_Plot <- Countries_Data_Plot %>% arrange(group,value)
Countries_Data_Plot$id <- seq(1, nrow(Countries_Data_Plot))

@@

# Top n of each group label
Top_Countries <- Countries_Data_Plot %>% 
  group_by(group) %>% 
  top_n(5,value)

# Create labels for all but top 5
label_data <- Countries_Data_Plot 
number_of_bar <- nrow(label_data)
angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust <- ifelse( angle < -90, 1, 0)
label_data$angle <- ifelse(angle < -90, angle+180, angle)

@@

# prepare a data frame for base lines
base_data <- Countries_Data_Plot %>% 
  group_by(group) %>% 
  summarize(start=min(id), 
            end=max(id) - empty_bar, 
            median = median(value, na.rm = T)
            ) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

@@

Discrete_Data_Plot <- Discrete_Data_Plot %>% 
  left_join(Countries_Data_Plot,
            by =c("individual","group")
  ) %>%
  mutate(value = ifelse(value.x <= -100,-100,value.x)) %>%
  select(individual,group,value,id) %>%
  arrange(group,value)

@@

Discrete_Data_Plot %>% 
  anti_join(Countries_Data_Plot,
            by = c("individual","group","id"))

@@

# Global Variables
Seq_axis <- seq(-100,100,20)
Plot_Limit <- max(Countries_Data_Plot$value,na.rm=T)
Plot_Limit_Low <- -110
Ticks_Color <- "grey50"

@@

ggplot(Countries_Data_Plot,

@@

           x = rep(max(Countries_Data_Plot$id),length(Seq_axis)),

@@

@@

# Number of countries shared by each Species
Species_Trans <- Tresholded_T_Data %>% 
  group_by(TaxonKey) %>% 
  summarise(
    n_countries = length(unique(Territory))
  ) %>% 
  left_join(Exploited_Species) %>%
  left_join(Spp_Clasification)

@@

Species_Data <- Tresholded_T_Data %>% 
  group_by(TaxonKey) %>% 
  summarise(n_trans_spp = length(unique(Territory))) %>% 
  left_join(Exploited_Species) %>%
  rename(scientific_name = TaxonName) %>% 
  left_join(Species_environ_list) %>%
  mutate(DemersPelag = ifelse(is.na(DemersPelag),"Other",paste(DemersPelag)),
         n_trans_spp = ifelse(n_trans_spp > 100, 100, n_trans_spp)) %>% 
  select(individual=scientific_name,
         value = n_trans_spp,
         group = DemersPelag) %>% 
  arrange(group,value) %>% 
  filter(value > 20) # remove all species under 10 (way too many to plot!)

@@

Seq_axis_spp <- seq(20,100,20)
Plot_Limit <- max(Species_Data$value,na.rm=T)

# Make the plot
ggplot(Species_Data, 
       aes(x=as.factor(id), 
           y=value,
           fill=group)
       ) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
  geom_bar(aes(x=as.factor(id),
               y=value,
               fill=group),
           stat="identity",
           alpha=0.5) +
  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
  # Add median lines for each gropup
  geom_segment(data=median_data, aes(x = end, y = median, xend = start+5, yend = median, colour = group),
               alpha=1, size=0.5 , inherit.aes = FALSE ) +
  # Add text showing the value of each line
  annotate("text", 
           x = rep(max(Species_Data$id),5),
           y = Seq_axis_spp,
           label = c(Seq_axis_spp[-5],">100"),
           color=Ticks_Color, 
           size=3 , 
           angle=0, 
           fontface="bold",
           hjust=1) +
  geom_bar(aes(x=as.factor(id),
               y=value,
               fill=group),
           stat="identity",
           alpha=0.5) +
  geom_text(data=label_data_rest,
            aes(x=id, y=101,
                label=individual,
                hjust=hjust), 
            color="black",
            fontface="italic",
            alpha=1,
            size=2.5,
            angle= label_data_rest$angle,
            inherit.aes = FALSE) +
  # Bold top 3 
  geom_text(data=Top_label_data,
            aes(x=id, y=101,
                label=individual,
                hjust=hjust), 
            color="black",
            fontface="bold.italic",
            alpha=1,
            size=2.5,
            angle= Top_label_data$angle,
            inherit.aes = FALSE) +
  # Add base line information
  geom_segment(data=base_data, 
               aes(x = start, 
                   y = -5, 
                   xend = end, 
                   yend = -5
                   ), 
               colour = "black",
               alpha=0.8, 
               size=0.6 , 
               inherit.aes = FALSE) +
  ylim(-100,110) + # sets the circle the first value the central the last value how wide
  theme_minimal() +
  theme(
    legend.position = c(0.5,0.5),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm") 
  ) +
  coord_polar() + 
  scale_fill_manual("Ecosystem Preference",
                    values = c(wes_palette(n = 4, name = "GrandBudapest1"),
                               wes_palette(n = 4, name = "GrandBudapest2")
                    ),
                    na.value = "white"
  ) +
  scale_colour_manual("Ecosystem Preference",
                      values = c(wes_palette(n = 4, name = "GrandBudapest1"),
                                 wes_palette(n = 4, name = "GrandBudapest2")
                      ),
                      na.value = "white"
  )
# 
ggsave(
    plot = last_plot(),
    width = 12,
    height = 12,
    units = "in",
    filename = "Species_circular_over20.png",
    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
  )

@@

# Sensitivity Analysis

```{r Sensitivity_Area_Treshold, eval = T, echo = F}

Area_Index_Level <- seq(.1,0.5,0.1)

p <- list()
i = NULL

for(i in 1:length(Area_Index_Level)){

  data <- Clean_Results_Trans %>% 
    filter(
      Area_Index >= Area_Index_Level[i],
      Area_Index <= 1-Area_Index_Level[i],
      Model_Index == MI
    ) %>% 
    group_by(Territory) %>% 
    summarise(
      n_trans_spp = length(unique(TaxonKey)),
      n_Neighbours = length(unique(Neighbour)),
      Trans_Rate = n_trans_spp/n_Neighbours
    )

  Median_data <- median(data$n_trans_spp)
  print(Median_data)

  p[[i]] <- ggplot(data) +
    geom_histogram(aes(n_trans_spp),
                   binwidth = 10, 
                   colour = "white"
    ) +
    labs(
      x = "Transboundary species (n)",
      y = "Frequency of EEZs",
      title= paste("Using a",(Area_Index_Level[i]*100),"% area treshold. (Median",Median_data,")")
    ) +
    # ggtitle(paste("Using a",(Area_Index_Level[i]*100),"% area treshold. (Median",Median_data,")")) +
    ggtheme_plot()

ggsave(
    plot = do.call(gridExtra::grid.arrange,p),
    width = 8,
    height = 8,
    units = "in",
    filename = "Area_Tresholds.png",
    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Sensitivity_Analysis"
  )

#Problem solving
